Distinguishing among coalescent models using two-site allele frequency spectra

### 2018-08-13 manuscript/manuscript.tex
Add some references.

In addition to the average SFS used to fit the model, we computed the average 2-SFS for pairs of sites at distances distances between 3~bp and 5~Kb.
Because we are using four-fold degenerate sites, we only computed the 2-SFS for distances that are multiples of 3.
For comparison between data and simulations, we scale the distances in basepairs by a critical distance $d_c = (r\E{T_2})^{-1}$.
We used a genome-wide recombination rate of $r = 2 \times 10^{-8}$ per basepair per generation \autocite{dmelrec}.
We estimated $\E{T_2}$ by $\pi / 2 \mu$.
For $\pi$, we used the average pairwise diversity at fourfold degenerate sites in the central region of each chromosome arm.
For $\mu$, we used a genome-wide mutation rate of $3 \times 10^{-9}$ per basepair per generation \autocite{dmelmu}.
These estimates are not precise, but only serve to scale genetic distances to the right order of magnitude.

>>>>

In addition to the average SFS used to fit the model, we computed the average 2-SFS for pairs of sites at distances distances between 3~bp and 5~Kb.
Because we are using four-fold degenerate sites, we only computed the 2-SFS for distances that are multiples of 3.
For comparison between data and simulations, we scale the distances in basepairs by a critical distance $d_c = (r\E{T_2})^{-1}$.
We used a genome-wide recombination rate of $r = 2 \times 10^{-8}$ per basepair per generation \autocite{ComeronEtAl2012}.
We estimated $\E{T_2}$ by $\pi / 2 \mu$.
For $\pi$, we used the average pairwise diversity at fourfold degenerate sites in the central region of each chromosome arm.
For $\mu$, we used a genome-wide mutation rate of $3 \times 10^{-9}$ per basepair per generation \autocite{KeightlyEtAl2014}.
These estimates are not precise, but only serve to scale genetic distances to the right order of magnitude.
